Title of the document here

### 2015-02-06 rmtw/assignment_1/assignment_1.tex
Finished threats

Threat - Open groups. No control over who is in them so potentially we can have respondants who are not knowledgeable answering questions.

>>>>

The fact that the questionnaire was distributed online via facebook groups also meant that there was another threat to the validty of the responses. These groups are not offically controled by the university and as such admission into these groups is up to the students who are organising them. This means that there is potential that some of the responses came from people not within the SE\&M isntitutions and this should be taken into consideration when analysing the results.
